Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness

### 2023-04-01 outputs/paper/paper.qmd
Add files via upload

# Model

@@

The [@tbl-lm], which is based the equation of @eq-model :

>>>>

# Model : Linear Regression

@@

In @eq-model:

-   ${\hat{Y}}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
-   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
-   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ , ${\hat{\beta_4}}$ , ${\hat{\beta_5}}$ and ${\hat{\beta_6}}$ are the estimated coefficients for each independent variable. These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant.
The independent variables are:
-   $X_{age}$ : Age of the individual.
-   $X_{degree-score}$ : A measure of the individual's level of education or degree. 
-   $X_{finance-score}$ : A measure of the individual's financial stability or status.
-   $X_{health-score}$ : A measure of the individual's overall health.
-   $X_{divorce-score}$ : A measure of the individual's likelihood of divorce or past divorces.
-   $X_{babies-number}$ : The number of babies/children the individual has.

The purpose of this multiple linear regression model is to understand the relationship between these independent variables and the dependent variable. By fitting the model to a dataset, we can estimate the coefficients and make predictions for new observations. we can also use the model to identify which independent variables have the most significant impact on the dependent variable and determine the strength and direction of those relationships.The [@tbl-lm], which is based the equation of @eq-model :
